Covariate Analysis of ROSMAP Reprocessed counts Regressing out Diagnosis as well for TWAS

### 2019-10-07 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
Finalize Data Processing

### Load Libraries
```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## It is assumed your working directory is where this file
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(synapser)
library(knitr)
library(doParallel)
library(foreach)
library(githubr)

cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

```{r synLogin}
synLogin()
```

### Data download
Obtain count matrix and metadata from synapse
```{r download.data}
# Download expression data
COUNT_ID <- 'syn8691134';
ALL_USED_IDs <- COUNT_ID
COUNT_OBJ <- synGet(COUNT_ID, version = 1)
COUNT <- read.table(COUNT_OBJ$path, header=T, sep='\t', check.names = F, row.names = 1)
COUNT[,grep('150_120419', colnames(COUNT))[2]] = NULL
# Convert rownames of counts from tracking id to ensemble gene id
tmp = data.frame(Gene.ID = rownames(COUNT)) %>%
  dplyr::mutate(ID = Gene.ID) %>%
  tidyr::separate(ID, c('ensembl_gene_id', 'position'), sep = '\\.')
rownames(tmp) = tmp$Gene.ID
rownames(COUNT) = tmp[rownames(COUNT), 'ensembl_gene_id']
# Get clinical metadata
METADATA.CLINICAL_ID <- 'syn3191087'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.CLINICAL_ID
METADATA.CLINICAL_OBJ <- synGet(METADATA.CLINICAL_ID, version = 3)
METADATA.CLINICAL <- read.table(METADATA.CLINICAL_OBJ$path,sep=',',header=T)
# Get clinical metadata with uncensored ages
METADATA.CLINICAL_ID1 <- 'syn7116000'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.CLINICAL_ID1
METADATA.CLINICAL_OBJ1 <- synGet(METADATA.CLINICAL_ID1, version = 1)
METADATA.CLINICAL1 <- read.table(METADATA.CLINICAL_OBJ1$path,sep=',',header=T)
# Get technical covariates
METADATA.TECH_ID <- 'syn4300313'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.TECH_ID
METADATA.TECH_OBJ <- synGet(METADATA.TECH_ID, version = 1)
METADATA.TECH <- read.table(METADATA.TECH_OBJ$path,sep='\t',header=T)
# Get picard metrics from synapse
METADATA.PICARD_ID <- 'syn8698240';
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD_ID
METADATA.PICARD <- synGet(METADATA.PICARD_ID, version = 2)$path %>%
  data.table::fread() %>%
  dplyr::rename(Sampleid = sample)
# Fix error in technical covariates data
KEY_ID <- 'syn3382527'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = KEY_ID  
KEY <- synGet(KEY_ID, version = 7)$path %>%
  read.csv %>% 
  dplyr::filter(!is.na(rnaseq_id)) %>%
  dplyr::select(projid, rnaseq_id) %>%
  tidyr::separate(rnaseq_id, c('a','b','batch'), sep = '_') %>% 
  unite(Sampleid, a, b) %>%
  dplyr::select(-batch) %>%
  unique
# Match technical and clinical covariates
METADATA <- METADATA.TECH %>%
  dplyr::left_join(METADATA.PICARD) %>%
  dplyr::select(-projid) %>%
  dplyr::left_join(KEY) %>%
  dplyr::left_join(METADATA.CLINICAL) %>%
  dplyr::select(-age_first_ad_dx, -age_death, -age_at_visit_max) %>%
  dplyr::left_join(METADATA.CLINICAL1)
# Pick higher quality RIN batch for sample 492_120515
METADATA <- METADATA %>%
  dplyr::group_by(Sampleid) %>%
  dplyr::top_n(1, RINcontinuous)
colnames(METADATA) = gsub('AlignmentSummaryMetrics__','',colnames(METADATA))
colnames(METADATA) = gsub('RnaSeqMetrics__','',colnames(METADATA))
# Get gene specific parameters from synapse
GENE.PARAM = synGet('syn8449369', version = 2)$path %>%
  data.table::fread(data.table = FALSE)
ALL_USED_IDs = c(ALL_USED_IDs, 'syn8449369')
GENE.LEN = dplyr::select(GENE.PARAM, ensembl_gene_id, gene.length) %>% 
  unique() 
rownames(GENE.LEN) = GENE.LEN$ensembl_gene_id
GENE.GC = dplyr::select(GENE.PARAM, ensembl_gene_id, percentage_gc_content) %>% 
  unique() 
rownames(GENE.GC) = GENE.GC$ensembl_gene_id 
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn20798011';
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
thisFileName <- 'ROSMAP_RegressDiagnosis_4_TWAS.Rmd'
# Github link
thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

@@

# Code WTF is this??
CODE <- Folder(name = "ROSMAP", parentId = parentId)
CODE <- synStore(CODE)

#Set Used SynIDs For Provenance
Syns_Used <- c("syn3382527", "syn4300313", "syn8449369", "syn7116000",
  "syn8691134", "syn3191087", "syn8698240"
)

# Set annotations
all.annotations = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'RNAseq',
  tissueTypeAbrv	= 'DLPFC', 
  study = 'ROSMAP', 
  organism = 'HomoSapiens',
  consortium	= 'ROSMAP',
  normalizationStatus	= TRUE,
  normalizationType	= 'CQN',
  rnaquantification = 'RSEM',
  genomeAssemblyID = 'GRCh37'
)

# Store SVA results
write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
ENRICH_OBJ = File('ROSMAP_SVA_Diagnosis_Corrected.tsv', 
                  name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'residualGeneExpForeQTL'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
write.table(COVARIATES, file = 'ROSMAP_SVA_Diagnosis_Covariates.tsv', row.names = F, sep = '\t', quote=F)
ENRICH_OBJ = File('ROSMAP_SVA_Diagnosis_Covariates.tsv', 
                  name = 'Covariates', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'covariates'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', 
                  name = 'Counts (filtered raw)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'filteredCounts'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store Estimated counts
NEW.COUNTS %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', 
                  name = 'Counts (estimated)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'estimatedCounts'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store logCPM
CQN.GENE_EXPRESSION$y %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', 
                  name = 'Counts (filtered logCPM)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'filteredLCPM'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', 
                  name = 'Gene length and GC content offset', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'offset'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store design matrix
MODEL1 %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', 
                  name = 'Design Matrix', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'designMatrix'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store surrogate variables
SURR.VAR %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', 
                  name = 'Surrogate Variables', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'surrogateVariables'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store residual gene expression for network analysis
RESIDUAL.NET.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', 
                  name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

#stopCluster(cl)
```

### R Source Code
[Github](`r thisFile`)

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
library(synapser)
library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "/home/jgockley/TWAS/code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd",
                                          parentId ="syn20798011",
                                          folderName = 'ROSMAP')
```

>>>>

### Load Libraries
```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## It is assumed your working directory is where this file
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(knitr)
library(doParallel)
library(foreach)
library(githubr)
cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

### Data download
Obtain count matrix and metadata from synapse
```{r download.data}
# Download expression data
COUNT_ID <- 'syn8691134';
ALL_USED_IDs <- COUNT_ID
COUNT_OBJ <- syn_temp$get(COUNT_ID, version = 1)
COUNT <- read.table(COUNT_OBJ$path, header=T, sep='\t', check.names = F, row.names = 1)
COUNT[,grep('150_120419', colnames(COUNT))[2]] = NULL
# Convert rownames of counts from tracking id to ensemble gene id
tmp = data.frame(Gene.ID = rownames(COUNT)) %>%
  dplyr::mutate(ID = Gene.ID) %>%
  tidyr::separate(ID, c('ensembl_gene_id', 'position'), sep = '\\.')
rownames(tmp) = tmp$Gene.ID
rownames(COUNT) = tmp[rownames(COUNT), 'ensembl_gene_id']
# Get clinical metadata
METADATA.CLINICAL_ID <- 'syn3191087'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.CLINICAL_ID
METADATA.CLINICAL_OBJ <- syn_temp$get(METADATA.CLINICAL_ID, version = 3)
METADATA.CLINICAL <- read.table(METADATA.CLINICAL_OBJ$path,sep=',',header=T)
# Get clinical metadata with uncensored ages
METADATA.CLINICAL_ID1 <- 'syn7116000'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.CLINICAL_ID1
METADATA.CLINICAL_OBJ1 <- syn_temp$get(METADATA.CLINICAL_ID1, version = 1)
METADATA.CLINICAL1 <- read.table(METADATA.CLINICAL_OBJ1$path,sep=',',header=T)
# Get technical covariates
METADATA.TECH_ID <- 'syn4300313'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.TECH_ID
METADATA.TECH_OBJ <- syn_temp$get(METADATA.TECH_ID, version = 1)
METADATA.TECH <- read.table(METADATA.TECH_OBJ$path,sep='\t',header=T)
# Get picard metrics from synapse
METADATA.PICARD_ID <- 'syn8698240';
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD_ID
METADATA.PICARD <- syn_temp$get(METADATA.PICARD_ID, version = 2)$path %>%
  data.table::fread() %>%
  dplyr::rename(Sampleid = sample)
# Fix error in technical covariates data
KEY_ID <- 'syn3382527'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = KEY_ID  
KEY <- syn_temp$get(KEY_ID, version = 7)$path %>%
  read.csv %>% 
  dplyr::filter(!is.na(rnaseq_id)) %>%
  dplyr::select(projid, rnaseq_id) %>%
  tidyr::separate(rnaseq_id, c('a','b','batch'), sep = '_') %>% 
  unite(Sampleid, a, b) %>%
  dplyr::select(-batch) %>%
  unique
# Match technical and clinical covariates
METADATA <- METADATA.TECH %>%
  dplyr::left_join(METADATA.PICARD) %>%
  dplyr::select(-projid) %>%
  dplyr::left_join(KEY) %>%
  dplyr::left_join(METADATA.CLINICAL) %>%
  dplyr::select(-age_first_ad_dx, -age_death, -age_at_visit_max) %>%
  dplyr::left_join(METADATA.CLINICAL1)
# Pick higher quality RIN batch for sample 492_120515
METADATA <- METADATA %>%
  dplyr::group_by(Sampleid) %>%
  dplyr::top_n(1, RINcontinuous)
colnames(METADATA) = gsub('AlignmentSummaryMetrics__','',colnames(METADATA))
colnames(METADATA) = gsub('RnaSeqMetrics__','',colnames(METADATA))
# Get gene specific parameters from synapse
GENE.PARAM = syn_temp$get('syn8449369', version = 2)$path %>%
  data.table::fread(data.table = FALSE)
ALL_USED_IDs = c(ALL_USED_IDs, 'syn8449369')
GENE.LEN = dplyr::select(GENE.PARAM, ensembl_gene_id, gene.length) %>% 
  unique() 
rownames(GENE.LEN) = GENE.LEN$ensembl_gene_id
GENE.GC = dplyr::select(GENE.PARAM, ensembl_gene_id, percentage_gc_content) %>% 
  unique() 
rownames(GENE.GC) = GENE.GC$ensembl_gene_id 
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn20798011';
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
thisFileName <- 'ROSMAP_RegressDiagnosis_4_TWAS.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

@@

CODE <- syn_temp$store(synapseclient$Folder(name = "ROSMAP", parentId = parentId))

#Set Used SynIDs For Provenance
Syns_Used <- c("syn3382527", "syn4300313", "syn8449369", "syn7116000",
  "syn8691134", "syn3191087", "syn8698240"
)
# Set annotations
all.annotations = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'RNAseq',
  tissueTypeAbrv	= 'DLPFC', 
  study = 'ROSMAP', 
  organism = 'HomoSapiens',
  consortium	= 'ROSMAP',
  normalizationStatus	= TRUE,
  normalizationType	= 'CQN',
  rnaquantification = 'RSEM',
  genomeAssemblyID = 'GRCh37'
)
# Store SVA results
write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'residualGeneExpForeQTL'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
write.table(COVARIATES, file = 'ROSMAP_SVA_Diagnosis_Covariates.tsv', row.names = F, sep = '\t', quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Diagnosis_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'covariates'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'filteredCounts'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store Estimated counts
NEW.COUNTS %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'estimatedCounts'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store logCPM
CQN.GENE_EXPRESSION$y %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'filteredLCPM'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'offset'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store design matrix
MODEL1 %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'designMatrix'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store surrogate variables
SURR.VAR %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'surrogateVariables'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store residual gene expression for network analysis
RESIDUAL.NET.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

stopCluster(cl)
```

```{r DelFiles, echo=T, results='hide'}
system('rm *.tsv')
```
### R Source Code
[Github](`r thisFile`)

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()

setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")

createAndKnitToFolderEntityClient(file = "ROSMAP_RegressDiagnosis_4_TWAS.Rmd",
                                          parentId ="syn20798011",
                                          folderName = 'ROSMAP')

```
